---
name: Luisa M.
surname: Mimmi
position: Public Policy & Data Analysis
address: EU citizen (Italy) | Green card holder
www: lulliter.com
email: lmm76@georgetown.edu
linkedin: luisa-m-mimmi
twitter: lulliter
github: lulliter
researchgate: Luisa-Mimmi
headcolor: 0088cc #cc0066 # 0088cc #0073e6 #990000
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: |-
  I am an economist by training with demonstrated expertise designing and implementing diagnostic tools, advanced analytics and data visualizations applied to economic development. Most of my research revolves around different policies improving universal access to basic infrastructure services (housing, water and sanitation, energy, education and health). 
    I am passionate about using data from different sources –including social media, GIS and satellite imagery– to understand and tackle complex public policy issues. 
profilepic: ../foto/LulaSalvador2015.jpg
docname: Curriculum Vitae
output:
  vitae::awesomecv: 
  keep_tex: false
  latex_engine: "xelatex" # maybe redund bc in awsomecv is already this 
always_allow_html: yes
header-includes:
  \usepackage{float}
  \usepackage{multicol}
  \usepackage{colortbl}
  \arrayrulecolor{white}
  \usepackage{hhline}
  \definecolor{light-gray}{gray}{0.95}
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# if (cond) expr
if (!require("pacman")) install.packages("pacman")
p_load('vitae'     # The CV's LaTeX Template
       ,'tibble'    # Data structure for tribbles
       ,'dplyr' , 'ggplot2'
       ,'lubridate'
       ,'magrittr'  # The Pipe %>%
       ,'here'      # Relative File Paths
       ,'readr'     # Data Loading
       ,'glue'      # String Manipulation
       ,'rorcid'
       ,'RefManageR'
       ,'scholar'
       , 'emojifont'
       #, 'fontawesome'
       , 'ggrepel' 
       ,'kableExtra'
       ,'huxtable'
       ,'gridExtra'
)

        # library(vitae)
        # library(ggplot2)
        # library(dplyr)
        # library(sf)
        # library(rworldmap)
        # library(stplanr)
        # library(ggrepel)
        # library(emojifont)
        # library(fontawesome)
        # library(kableExtra)
        # library(huxtable)
        # library(gridExtra)

p_load_gh("rstudio", "fontawsome")

 # MODO ALTERNATIVO -----------------------
# require(xfun)
# packages <- c('vitae'     # The CV's LaTeX Template
#              ,'tibble'    # Data structure for tribbles
#              ,'dplyr' 
#              ,'lubridate'
#              ,'magrittr'  # The Pipe %>%
#              ,'here'      # Relative File Paths
#              ,'readr'     # Data Loading
#              ,'glue'      # String Manipulation
#              ,'rorcid'
#              ,'RefManageR'
#              ,'scholar'
#              )
# xfun::pkg_attach2(packages, message = FALSE)
 
# data input (in "./data/data_Lula.r")
source(file = here("data", "data_Lula.r")) # "data.r"



# rorcid_app <- httr::oauth_app(
#   appname = "rorcid",
#   key = "APP-7E02XXWNQBFNMG1B",
#   secret = "74c15780-e323-48a0-9296-ecceaf46e447"
# )

# ORCID_TOKEN <- Sys.getenv("ORCID_TOKEN") 
```

<!-- # Employment history -->

\faIcon{briefcase} Professional Experience
============================================

```{r employment, results='asis'}
# tribble(
#   ~Years, ~Position, ~Company,
#   '2018:...', "Research Fellow", "Inter-American Development Bank, (Washington DC)",
#   '2018:...', "Fundraising Data Analyst (Pro bono)", "New York Encounter, (remote)",
#   '2009:2018', "Senior M&E Specialist", "World Bank, Sustainable Development VP, (Washington DC)",
#   '2008' , "Policy Analyst", "Inter-American Development Bank, (Washington DC)",
#   '2007' , "Summer Intern", "AVSI International (Brazil)",
#   '2001:2006', "Business Intelligence Analyst", "Value Partners (Italy)",
#    ) %>%
#   # arrange(-Years) %>%
#    #filter(Start > 2000) %>%
#   # mutate(End = replace_na(End, "")) %>%
#   # mutate(Years = paste(Start, "--", End, sep = "")) %>%
#   select(Years, Position, Company ) %>%
#   detailed_entries(
#     when = Years, 
#     what = Position, 
#     where = Company )


work %>%
  vitae::detailed_entries(
    with =  unit , #scambiati x spazio
    what = title,
     why = detail,
    when = glue::glue("{startMonth} {startYear}-{endMonth} {endYear}",.na = ""),
    where = where #scambiati x spazio
  )

```

\faIcon{lightbulb}  Other Professional Service
===================================== 
```{r}
# service <- tribble( ~what, ~when, ~with,
#   "Peer Reviewer",                "ongoing",                   "Energy Policy & Journal of the Association of Environmental 
  
  service %>%
  vitae::detailed_entries(
  what = what, 
  when =  when,
  why = why  
  )
  
```

\bigskip

\faIcon{r-project}  Data Science Projects
===================================== 
```{r PROJECTS}
# ~area,  ~year, ~accomplishment, ~where, ~link,
# projects %>%
# detailed_entries(
#     with = area,
#     when =  year,
#     what = accomplishment, 
#     # where = where,
#         why = link,
#         .protect = FALSE, # to turn link in LATEX 
#   )


#projects2 <- tibble::tribble(~name,  ~year, ~explain,
projects2 %>%
vitae::detailed_entries(
    what = name,
    when = year,
    #with = NA_character_,
    why = explain,
    #where = NA_character_,
    .protect = FALSE
  )

 
```


<!-- # Education -->
```{r education}
# edu <- rorcid::orcid_works("0000-0002-2244-8282")
# edu$`0000-0002-2244-8282`$`education-summary` %>%
#   detailed_entries(
#     what = `role-title`,
#     when = glue::glue("{`start-date.year.value`} - {`end-date.year.value`}"),
#     with = organization.name,
#     where = organization.address.city
#   )
```

\faIcon{graduation-cap} Education
==================================
<!--  \faIcon{university} -->
```{r EDUCATION}
edu %>% 
  vitae::detailed_entries( with = inst,
    what = degree,
    why = detail,
    when =  ifelse(is.na(startYear),
                   endYear, glue::glue("{startYear}-{endYear}",.na = "")),
    where = where)
```


<!-- \endfirstpage -->

\faIcon{medal} Academic Honors
=============================== 
```{r}
# ~area, ~accomplishment, ~year, ~where, [~detail],
honors %>%
  vitae::detailed_entries(
    # with = area,
    # what = accomplishment,
    what = where   ,
    when = year,
    with =glue::glue("{area}: {accomplishment}",.na = "" )
  )

# # try to make it less pompous
# honors %>% 
#   vitae::brief_entries(
#     #with = area,
#     what = glue::glue("{area} - {accomplishment}",.na = "" )  ,
#     #why = detail,
#     when = where ,
#     with = year
#   )
```


\faIcon{laptop-code} Software
=============================== 
<!-- \faIcon{file-code} -->
  
```{r}
# software %>%
#    vitae::detailed_entries(
#    what  = skills ,
#     with =  area,
#     where = detail #
#   )
#  
software %>%
   vitae::detailed_entries(
   what  = glue::glue("  {area}: [{skills}]")
    #,where = detail #
  )

# software %>%
#    vitae::brief_entries(
#    what  = area ,
#     with =  skills
#      
#   )
```


\faIcon{globe} Languages
==================================
```{r}
languages %>% 
  vitae::detailed_entries(
    what = glue::glue("{area}: [{skills}]") 
    )
```

\newpage

\faIcon*{pencil} Courses and Training
===========================
 
```{r}
#courses <- tribble( ~area, ~accomplishment, ~year, [~where], [~detail],

courses %>% 
  vitae::detailed_entries(
    why = area ,
    what = accomplishment,
    when = year#,
    #why = detail
    
  )
    
```


<!-- FOR THESE I AM NOT ACTUALLY USING data_Lula.r [I extract from .bib directly using `vitae::bibliography_entries` own function ] -->

\faIcon*{calendar} Talks
===========================
  
```{r TALKzotero}
# # from Synched Lula-MyTalks.bib (in Zotero)
# author, title, type, issued, journal
 
  vitae::bibliography_entries(file = here::here("data", "Lula-MyTalks.bib")
                             # ,sorting="ydnt"
                              ) %>% 
  arrange(desc(issued))

```

\newpage

\faBook[regular] Publications
===========================
[_See detailed list on [**my Google Scholar Profile**](https://scholar.google.com/citations?user=OBYla5gAAAAJ&hl=en&oi=ao)_]

\faBookOpen[regular] Peer-Reviewed Articles & Technical Reports
---------------------------

```{r PUBgooglesch}
# # from Google Scholar
# publicationsGSL  %>%
#   vitae::detailed_entries(
#     what = title,
#     when = year,
#     with = author,
#     where = journal #,
#     #why = glue::glue("citations: {cites}")
#   )
#     
```

```{r PUBzotero}
# # from Synched Lula-MyPublications-Narrow.bib (in Zotero)
# author, title, type, issued, journal
 
 vitae::bibliography_entries(file = here::here("data", "Lula-MyPublication-Narrow.bib")
                             # ,sorting="ydnt"
                              ) %>% 
  arrange(desc(issued)) %>% 
  filter( stringr::str_detect(type ,"webpage" , negate = TRUE)  )
 
```


\faIcon{rss} Other Media
---------------------------

<!-- \faIcon{file-signature} -->
```{r BLOGzotero}
# # from Synched Lula-MyPublications-Narrow.bib (in Zotero)
# author, title, type, issued, journal
 
#print<-  
vitae::bibliography_entries(file = here::here("data", "Lula-MyPublication-Narrow.bib")
                             # ,sorting="ydnt"
                              ) %>% 
     arrange(desc(issued)) %>% 
  filter( stringr::str_detect(type ,"webpage" )  )
 

# --------- names(print)
#   "URL" "author"  "genre" "id" "issued" "keyword" "language"  "publisher"  "title"            "title-short"  "type" "DOI" "ISSN" "accessed" "container-title"  "issue""page" "volume"           "abstract"  "collection-title" "number" "publisher-place"  "annote"  

# --------- print$type
# "webpage" "webpage" "report" "webpage" "webpage" "article-journal" "report"         
#  [8] "report"          "report"          "article-journal" "report"          "webpage"     
```








```{r copyTOCVDIR, message=FALSE, warning=FALSE, include=FALSE}
# here::here()
# 
# # ObjectiFY SubDirs	
# from.dir <- "./content/cv/cv_making/resume_twentysecond"
# fs::path_abs(from.dir)
# 
# to.dir   <- "./content/cv"
# fs::path_abs(to.dir)
# 
# # List Files 
# files <- list.files(path = from.dir, 
# 						  pattern='\\.pdf$', # an optional regular expression. (ends with
# 						  full.names = TRUE, # If TRUE, the directory path is prepended to the file names 
# 						  recursive = FALSE) # Should the listing recurse into directories?
# 	
# # all_munge <- list.files(path = "./03_Munge/", pattern = '\\.R$' , 
# #                         all.files = FALSE,  # def (= only visible)
# #                         full.names = FALSE, # def (= no dir name prepended)
# #                         recursive = FALSE,  # def  (= no inside sub-dir )
# #                         ignore.case = TRUE, #    (= pattern-matching be case-insensitive)
# #                         include.dirs = FALSE, # def (subdirectory names NOT be included in recursive listings)
# #                         no.. = FALSE) # def (both "." and ".." be excluded also from non-recursive listings)
# class(files) 
# 
# # function to MOVE
# for (f in files) file.copy(from = f, to = to.dir,	 overwrite = T, copy.date = T)
```



